sensiAnPaper1All

### 2015-07-07 sensiAnPaper1All.Rmd
more sensitivity testing

<!-- eval=FALSE to stop slow code being executed --> 
```{r, eval=FALSE}
  library(resistance)

  outFolder <- "C:\\Dropbox\\resistanceResults\\"

@@

  ## to load previously saved runs, e.g. these that I added 100 onto filename
  load(file=paste0(outFolder,'listOutMix_100.rda'))
  load(file=paste0(outFolder,'listOutI1_100.rda'))
  load(file=paste0(outFolder,'listOutI2_100.rda'))

@@

  #check1
  #plot the 2 individual results & the mixture, just to check what is going on
  #the mixture one looks superficially similar to the individual ones superimposed
  x11()
  plotallele.freq.andy(listOutMix)
  x11()
  plotallele.freq.andy(listOutI1)
  x11()
  plotallele.freq.andy(listOutI2)

@@

@@

### do tree analysis
```{r}
  require(rpart)

>>>>

```{r}
  library(resistance)

  outFolder <- "C:\\Dropbox\\resistanceResults\\"
```

<!-- eval=FALSE to stop slow code being executed --> 
```{r, eval=FALSE}

@@

```{r}
  ## to load previously saved runs, e.g. these that I added 100 onto filename
  load(file=paste0(outFolder,'listOutMix_100.rda'))
  load(file=paste0(outFolder,'listOutI1_100.rda'))
  load(file=paste0(outFolder,'listOutI2_100.rda'))

@@

  #check1
  #plot the 2 individual results & the mixture, just to check what is going on
  #the mixture one looks superficially similar to the individual ones superimposed
  #x11()
  plotallele.freq.andy(listOutMix)
  #x11()
  plotallele.freq.andy(listOutI1)
  #x11()
  plotallele.freq.andy(listOutI2)

  #I should be able to compare single scenarios
  #yes this works, but not too useful
  plotallele.freq.andy( list(results=list(listOutMix$results[[1]], listOutI1$results[[1]] )) )
  #this is a modifdeied version of Beths function
  #allowing curtis fig2 to be applied to any scenario
  plotcurtis_f2_generic( listOutMix$results[[1]], listOutI2$results[[1]], listOutI1$results[[1]] )

@@

  # comparing sensitivity inputs to those used by Beth to reproduce curtis fig2
  inputCurtis <- createInputMatrix(FALSE)
  inputSensiMix <- listOutMix$input

  input <- cbind(inputCurtis, inputSensiMix)
  write.csv(input, file=paste0(outFolder,'inputCurtisSensiCompare.csv'))

@@

### do tree analysis
```{r, eval=FALSE}
  require(rpart)
